Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{ This work has been supported by the Italian PRIN Project COMMON-WEARS (2020HCWWLP) and the EU/MUR FSE REACT-EU PON R\&I 2014-2020. }

### 2023-05-21 paper-2023-acsos-pulverization.tex
Assure the reader we'll explain those terms

From the previous section,
we can identify three main pieces of information for the definition of a pulverised system and its deployment:
\begin{enumerate}[label=\it{(\roman*)}]
  \item the description of the logical system and its partitioning into components and deployment units;
  \item the definition of the \emph{target} deployment domain (\emph{infrastructure}), i.e., the specification of the \emph{requirements} posed on hosts in terms of required (or preferred) capabilities; and
  \item the definition of the \emph{deployment plan}, i.e., the allocation of the pulverised components to the infrastructural elements, together with constraints and reconfiguration policies.
\end{enumerate}
%
%Coherently with the \emph{single responsibility principle},
We capture these %two 
 descriptive needs into two distinct \acp{dsl}: the \dslSys{} and the \dslDep{}.
%
An overall view of the approach in terms of the provided tools and the main modelling concepts is provided in \Cref{fig:approach}.

>>>>

From the previous section,
we can identify three main pieces of information for the definition of a pulverised system and its deployment:
\begin{enumerate}[label=\it{(\roman*)}]
  \item the description of the logical system and its partitioning into components and deployment units;
  \item the definition of the \emph{target} deployment domain (\emph{infrastructure}), i.e., the specification of the \emph{requirements} posed on hosts in terms of required (or preferred) capabilities; and
  \item the definition of the \emph{deployment plan}, i.e., the allocation of the pulverised components to the infrastructural elements, together with constraints and reconfiguration policies.
\end{enumerate}
%
%Coherently with the \emph{single responsibility principle},
We capture these %two 
 descriptive needs into two distinct \acp{dsl}: the \dslSys{} and the \dslDep{}.
%
An overall view of the approach in terms of the provided tools and the main modelling concepts is provided in \Cref{fig:approach}: such elements are explained in the following sections.
